Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-09-28 manuscript/main.tex
revised proof

\textit{Sketch for a proof that SW alignment is globally optimal}

Notation $F_i$ is the alignment of size $i$ with $i = 1,2,...,(n + k - 1)$. $S(F_i)$ is the score of the alignment.

First show that the score in each cell is optimal:
\begin{enumerate}
\item There are three options for $F_1$ (Gap in $\mathcal{A}$, Gap in $\mathcal{B}$, . This alignment is optimal when $S(F_1)$ is maximized
\item Every alignment's score $S(F_i)$ with $i > 1$ when maximized, is composed of the score of the `one-shorter' alignment $S(F_{i-1})$ and the score of the $i$-th element. If not the score could be increased by choosing a different $F_{i-1}$ that has a higher score.
\item The dp matrix contains all possible alignments. Since every cell is optimal, the highest score in the dp matrix must be globally optimal
\end{enumerate}

>>>>

\textit{Proof that SW alignment is globally optimal}

$F_i$ is the alignment of size $i$ with $i = 1,2,...,(n + k - 1)$. $S(F_i)$ is the score of the alignment.

\begin{enumerate}
\item There are four options for $F_1$ (Gap in $\mathcal{A}$, Gap in
    $\mathcal{B}$, Mismatch, Match) . This alignment is optimal when $S(F_1)$ is maximized
\item Every alignment's score $S(F_i)$ with $i > 1$ when maximized, is composed of the score of the `one-shorter' alignment $S(F_{i-1})$ and the score of the $i$-th element. If not the score could be increased by choosing a different $F_{i-1}$ that has a higher score.
\item By induction therefore follows that every alignment represented in the
    dynamic programming matrix (\ref{fig:score_matrix}) and calculated according
        to Equations \ref{eqn:scoring} and \ref{eqn:fill} is an optimal alignment
    ending in the locations specified by the row and column index in the matrix.
\item The dynamic programming matrix contains all possible alignments. Since
    every cell is optimal, the highest score in the matrix must be globally
    optimal.
\end{enumerate}
